\chapter{Introduction}
\epigraph{``The most elementary single difference between the human mind and that of brutes lies in this deficiency on the brute's part to associate ideas by similarity.''}{William James, \textit{Principles of Psychology}}
Deep learning methods have achieved incredible success recently, reaching human-level performance in domains ranging from vision \citep[e.g.][]{Szegedy2015} to playing games \citep[e.g.][]{Silver2016}. However, these systems still lack some important human abilities \citep[e.g.][]{Lake2016}. Deep learning models are data-hungry, while humans can frequently learn from relatively few examples. Furthermore, even if they are given a large amount of data, deep learning systems may not be able to generalize well outside the data distribution they trained on. Finally, once knowledge is learned in the weights of a deep learning model, it is difficult to flexibly reuse that knowledge. From the perspective of William James (quoted above), most neural networks are brutes, which don't understand the similarity of new situations to their prior experiences, and so do not know how to flexibly respond to changes in their environment or goals. \par
By contrast, humans can use our knowledge flexibly. We can learn from few examples. We can introspect about our learned behavior to explain or change it. We can even remap our behavior in a way completely inconsistent with our prior behavior, such as trying to lose a game we have previously been trying to win \citep{Lake2016}. More generally, we are often able to accurately behave according to linguistic instructions without seeing examples of such behavior. All of these types of flexibility can be quite difficult for deep learning systems. \par 
This apparent contrast between humans and neural networks has raised questions about the validity of neural networks as a cognitive model for many years \citep[e.g.][]{Fodor1988}, and the recent successes of deep learning have only increased the frequency of these critiques \citep[e.g.][]{Lake2015, Lake2016, Lake2017, Marcus2018}. It is important to address these perspectives, and to understand how deep learning systems can be improved to serve as better models of human flexibility. There have been a number of attempts to address or integrate these critiques from a variety of perspectives \citep[e.g.][]{McClelland1999, McClelland2010}. In this paper, I will particularly focus on how these critiques overlook the benefits of transfer \citep{Lampinen2017a} and recent progress in deep learning \citep{Hansen2017}. In particular, deep learning research has made important progress on improving learning speed, generalization, and flexibility. However, even with contemporary methods there are many human-like abilities that remain frustratingly out of reach. \par
In the remainder of this paper, I will attempt to address these issues. I will first review some of the cognitive issues and the progress to date, and try to provide a unifying perspective on how various types of transfer contribute to human learning and flexibility. I will then show some of my prior research on this topic, including analyses of the effects of transfer in neural networks, explorations of flexibility and transfer in humans. Finally, I will propose some new directions for my research, including a set of studies exploring human flexibility in a new setting, and a new type of deep learning architecture that yields much greater flexibility. \par

\section{Area review: Cognitive flexibility}

What kind of flexibility do humans have? We are often able to learn rapidly. For example, we can achieve some competence in a novel video game within a few minutes \citep{Lake2016}. We can learn new concepts from seeing only a relatively small number of examples \citep[e.g.][]{Bourne1970}. We can often learn even faster if we can actively participate in the learning process by selecting examples rather than passively receiving them, especially if the concepts are simple enough that we can generate a good hypothesis space \citep{Markant2014a}. \par
We can then apply what we have learned to new situations. The studies of \citet{Bourne1970} that I referenced above show that once people have learned a new concept from examples, they can generalize that knowedge to learn structurally-similar new concepts more rapidly. Indeed, even without explicit awareness of the relationship between two tasks, humans can sometimes benefit from transfer effects \citep[e.g.][]{Day2011}. In general, human analogical transfer abilities have been suggested to be a critical component of `` what makes us smart'' \citep{Gentner2003}. \par
Yet human flexibility is apparent beyond transfer between isomorphic tasks. We can often competently change our learned behavior in response to instruction or other goals, such as trying to lose a game we were previously trying to win, or trying to achieve some orthogonal task \citep{Lake2016}. Indeed, it has been known for almost a century that even other animals exhibit this sort of flexible knowledge use -- they engage in ``latent learning'' of environmental features that may be useful when solving future tasks \citep{Blodgett1929}. Both humans and other animals are capable of flexibly applying our knowledge in many situations.  \par
However, our flexibility is not universal. Sometimes it is quite difficult for us to integrate new knowledge. For example, even undergraduate students with substantial mathematical background often struggle with understanding new mathematical concepts.\footnote{I will focus on mathematical cognition for much of this paper. Although the phenomena I discuss are much more general, and I will include a number of other examples, mathematical cognition offers a unique microcosm of human abilities for transfer, abstraction and flexibility.} They may mistakenly assume the converse of a theorem, or get caught up in concrete ways of thinking about abstract concepts \citep{Hazzan1999}. Socrates' dialog about doubling the area of a square captures the misunderstandings that modern subjects make, just as it did for those over 2000 years ago, yet it does not help them to deeply understand the principle \citep{Goldin2011}. Even after engaging with the dialog, nearly 50\% of modern subjects failed at the simplest generalization of the principle: to a square of different size. Similarly, even students who complete a course in geometry in high school may not achieve formal deductive understanding of the concepts taught unless (or until) they become undergraduate mathematics majors \citep{Burger1986}. Furthermore, superficial details of how a concept is presented can have profound impacts on how easy it is to reason about, even if the underlying concept is exactly the same \citep[e.g.][]{Kotovsky1985, Kaminski2008, Lampinen2017b}. There is a wealth of research showing that our learning is far from universally flexible. \par 
We also often fail to flexibly use the knowledge we have. For example, even mathematics students who can correctly state a rule or theorem are not necessarily able to apply it to create a proof \citep{Weber2001}. Similarly, even if experimental subjects can learn a basic concept rapidly, it may be difficult for them to apply it in more abstract situations or to extract more formal understanding from it \citep[e.g.][]{Lampinen2017b}. Likewise, rapid analogical transfer is often only possible when superficial details match closely, or when subjects are explicitly told to transfer \citep[e.g.][]{Gick1980}. Because of findings like these, \citet{Detterman1993} has argued that inducing transfer requires manipulations ``with the subtlety of a baseball bat,'' and so we should conclude that ``significant transfer is probably rare and accounts for very little human behavior.'' This is a particularly tendentious presentation of the issues, but it captures the important broader insight that humans are not always rapid learners or flexible reasoners. \par 
How can we reconcile the demonstrations of rapid learning and flexibility with the evidence that some concepts are learned slowly and some knowledge is inflexible? How can we reconcile arguments that transfer is key to ``what makes us smart'' \citep{Gentner2003}, with arguments that ``significant transfer is probably rare and accounts for very little human behavior'' \citep{Detterman1993}? There are a variety of factors that affect whether transfer will occur \citep{Barnett2002, Lampinen2017a}. First, we need high-quality representations of the concepts we are learning in order to reason flexibly with them. These generalizable representations are generally created through making connections between different pieces of our knowledge \citep{Wilensky1991, Schwartz2015}. Second, we often need strategic meta-knowledge about where and how to apply our knowledge in new situations, which also must be learned \citep{Weber2001}. Both these factors mean that transfer may happen more easily over longer periods of time, as I have argued in my prior work \citep{Lampinen2017a}. The quality of the representations we have, and the way those representations relate to the new tasks we are presented with, both affect our ability to learn rapidly and reason flexibly. \par 

\subsection{Flexibility as transfer}
I argue that all these types of flexibility (and inflexibility) can be seen as transfer, defined broadly as the way that ``knowledge acquired in one situation applies (or fails to apply) in other situations.'' \citep{Singley1989}. From this definition it is clear that applying learned features and structures to learn faster in a new situation, as in \citet{Bourne1970}, is a type of transfer. I argue that in fact all rapid learning must rely on transfer of prior knowledge in order to constrain the hypothesis space under consideration. Even other types of flexibility, such as adapting to instructions, can be seen as transferring several different types of knowledge (prior knowledge about a task, other related taks, and language) to a new situation. For example, if we are asked to try to lose at chess, we are essentially presented a new task to which we need to transfer both our prior knowledge of chess and our prior knowledge of what ``trying to lose'' means. Thus flexibility and transfer are essentially two perspectives on the same broad phenomena. I will therefore use these words for different perspectives on this phenomenon. Specifically. I will use ``flexibility'' generally to refer to the behavioral phenomena, and ``transfer'' to refer to the computational principles underlying these phenomena. \par  
Why do we sometimes fail to be flexible? There are several reasons this can occur. First, we may not have the prior knowledge necessary to be flexible. We can't transfer what we don't know. Second, our representations may lack the quality necessary to transfer them. We often can't transfer what we don't know well \citep[c.f.]{Hazzan1999, Weber2001}. Third, we may not recognize that we have applicable prior knowledge to transfer \citep{Detterman1993}. Finally, we may actually have prior beliefs that do not apply to the present situation, and so transferring them will actually interfere with our ability to learn. This is generally called ``negative transfer'' \citep{Singley1989}. \par
For transfer to be beneficial overall, we must generally encounter settings where our prior knowledge is applicable, and furthermore we must have good ways of integrating that prior knowledge with new experiences. In the next section I will discuss some of the features that allow us to do so. \par

\subsection{What factors contribute to our flexibility?}
We need to address the computational question of how and when we can use transfer to behave flexibly. In this section I will give a brief overview of the contributing factors. \par 

\textbf{Complementary learning systems:} First, it has been proposed that we have complementary learning systems \citep{McClelland1995, Kumaran2016}. These complementary systems allow us to learn rapidly from new knowledge while avoiding catastrophic interference \citep{McCloskey1989} with the statistical knowledge we have accumulated over longer timescales. The key idea is that we have a slow (parametric) learning system which sets up good representations, while a fast (nonparametric) learning system stores new knowledge by using these representations. Throughout this paper, we will return to this theme of fast and slow learning which support each other. I will therefore divide the rest of this section into the ``slow'' and ``fast'' systems that contribute to transfer.\par
However, it's worth noting that ``slow'' vs. ``fast'' learning systems is not a strict dichotomy. This broad distinction is useful, but in reality learning systems fall on a continuum, and the time-course of learning in a given system is often dramatically affected by what knowledge is already present \citep[e.g.][]{McClelland2013}. Thus this dichotomy between learning systems should not be interpreted as a strict division. Instead, it is a useful way of highlighting the cooperation between distinct systems that operate across distinct, yet sometimes overlapping, timescales. \par 

\subsubsection{Slow}
In this section I will discuss the slow learning systems that contribute to transfer and flexibility. \par
\textbf{Culture \& education:} One critical contributor to transfer is culture. Our cultures have accumulated knowledge over extremely long time scales that allows us to advance much more rapidly now \citep{Tomasello1993, Bengio2012}. For example, mathematical concepts have been constructed by humans \citep{Hersh1997, MacLane1986}, and it has taken us millenia to construct subjects like calculus. Yet today many students gain fluency with these ideas before they graduate high school. Because culture has set up useful representations for these concepts, we are able to acquire them much more rapidly \citep[e.g.][]{McClelland2016}. Furthermore, culture has set up systems of education that are structured precisely to help us learn rapidly and generalize effectively. \par 
By contrast, if our culture does not represent or highlight certain concepts, we may struggle to reason about them. For example, one Amazonian tribe that lacks words for exact numbers shows substantially impaired ability to do basic tasks involving cardinality, which are interpreted as a fundamental deficit in the ability to represent exact cardinality at all \citep{Gordon2004}. Similarly, although the number line as a spatial representation of number appears relatively universal, cross-cultural and historical studies reveal that it is constructed rather than innate \citep{Nunez2011}. Culture helps set up powerful representations and metaphors for us to learn from. Without these representations, our learning would be substantially slower. \par 
\textbf{Transfer between tasks:} Even if culture has not explicitly highlighted (or engineered) structural relationships between tasks, we can benefit from structural similarity. For example, after learning an artificial grammar, subjects can generalize their knowledge to novel sequences from the same grammar applied to novel symbols \citep[e.g.][]{Tunney2001}. From learning about simple harmonic oscillators in the context of springs, participants can transfer to a superficially unrelated problem about controlling the population of a city \citep[e.g.][]{Day2011}. Because many tasks we perform share deep underlying structures, we can take advantage of transfer to learn faster on new tasks. \par 
\textbf{Grounding, embodiment, and representation quality:} One particular type of transfer that seems to be especially useful is grounding \citep{Barsalou2007}. In particular, conceptual representations often tend to be tied into more basic perceptual-motor systems, e.g. arithmetic in the Approximate Number System \citep{Park2013}, or mathematical (and other) reasoning in gestures \citep{Goldin-Meadow1993, Goldin-Meadow1999}. This sort of grounding can be very beneficial to understanding \citep{Nathan2008, Schwartz2015, Wakefield2018}. Because our perceptual-motor system have exceptionally good representations that are trained over long developmental time-scales, we may benefit from leveraging these representations to transfer our understanding to analogous conceptual domains. \par 
It is also worth considering that grounding and embodiment can hold us back. Even our understanding of symbolic expressions seems to be influenced by ``meaningless'' perceptual details like their spacing \citep{Landy2007}. It has also been argued that too concrete of examples can limit generalization \citep{Kaminski2008}, although the details of that particular demonstration have been debated \citep{DeBock2011, Lampinen2017b}. There is probably some negative transfer from grounding in some cases, but overall it is probably outweighed by the positive. \par
However, there are a number of conceptual issues that come along with grounding, such as how to define abstraction \citep{Dove2016}, and whether the grounding must be in the real-world, or can more generally be in concepts that are better understood \citep{Wilensky1991}, regardless of whether they are basic perceptuo-motor knowledge. The line between grounding and other types of transfer can be blurry, because, like many psychological ideas, its definitions are multifarious. \par 
The overlapping field of embodied cognition has raised the opposite issue, arguing that cognition cannot be considered at all outside of the physical, physiological, and social situations in which it is grounded \citep{Anderson2003}. Others have argued that even the computation metaphor in cognition is fundamentally flawed, because it neglects the fact that intelligence evolved in systems interacting with the world \citep{Cisek1999}, through a process of hierarchically constructed control systems \citep{Cisek2019}. It is important to keep these arguments in mind, and not to neglect the world in which our brains reside in favor of a disembodied, computational mind. \par 
\textbf{Rerepresentation and different kinds of knowledge:} The work of Karmiloff-Smith \citep[e.g.][]{Karmiloff-Smith1986, Karmiloff-Smith1992, Clark1993} focused on the idea that we repeatedly redescribe our internal knowledge, reorganizing it in order to better understand the world. To support this theory, she examined evidence of U-shaped developmental curves, where children would actually get worse at a task before they reached ceiling, often because they at first over-generalized a rule. She argues that this shows a pattern of systematic progression of knowledge from implicit representations to various stages of explicit ones which allow progressively more flexibility. In \citet{Karmiloff-Smith1986} she describes some particularly interesting evidence: children fail to balance an oddly shaped block when asked to do so, but successfully balance it when asked to build a house, because their procedural knowledge is more sophisticated than their explicit knowledge. \par 
This pattern of procedural knowledge proceeding more explicit or object-like knowledge is supported by a much broader literature, from the gesture results of \citet{Goldin-Meadow1993} referenced above to work suggesting that we progress from understanding mathematical concepts as processses to understanding them as objects \citep{Dubinsky1991, Hazzan1999}. If we do not already have good representations for a concept, we must create them by slow, procedural learning and reorganization, before we can begin to reason flexibly with the concept. However, it's worth noting that the process is bidirectional -- procedural knowledge supports conceptual understanding, but conceptual knowledge also helps improve procedural performance \citep{Rittle-Johnson2001}. Furthermore, procedural learning can occasionally be misleading. Getting too caught up in procedures that only work in simple cases can actually inhibit conceptual understanding \citep{McNeil2005}. There are sometimes trade-offs to transfer (see section \ref{fast_slow_interactions}). \par 
Is a separate rerepresentation process necessary to explain these phenomena? It is difficult to determine this. Often rapid transitions and rule-like behavior can be fully captured within neural networks or statistical learning models more generally \citep[e.g.][]{McClelland1999, McClelland2002, Schapiro2009, Aslin2012}. While \citet{Karmiloff-Smith1992} argues that these mechanisms can not explain U-shaped developmental trajectories, since error-correcting learning will not apply where there are no errors, she ignores the potential effects of all the other learning that children are simultaneously doing on other related tasks. Furthermore, some compression emerges naturally from the learning dynamics of gradient descent \citep{Tishby2015, Shwartz-Ziv2017, Achille2017}. It is difficult to rule out the possibility that U-shaped developmental trajectories can be explained by the combination of this compression and the effects of other learning on related tasks. \par
\textbf{Summary:} We accumulate knowledge throughout the course of our lives. Some of this knowledge is implicit in the statistics of the world around us, while some is culturally constructed and transmitted. The quality of our knowledge representations can be improved by connecting to other knowledge, or by grounding in perceptual-motor understanding. Once we have acquired sufficiently high-quality knowledge representations, we are often able to transfer when we encounter a new task, and thereby learn more effectively than we could from \textit{tabula rasa}. This improvement in learning manifests as both more efficient learning and better generalization. \par

\subsubsection{Fast}
In this section I will discuss the systems that contribute to fast learning and transfer. It's important to note that these are systems that can be applied rapidly, but are not necessarily learned rapidly. Indeed, many of these reasoning systems are themselves culturally constructed, and must thus be learned over development. \par
\textbf{Hippocampal:} From the complementary learning systems perspective, the hippocampus serves as a fast learning system which can store an essentially unlimited number of distinct experiences while minimizing interference, i.e. as a nonparametric learning sytem \citep{Kumaran2016}. This makes it an excellent sub-system for learning from a small amount of data, because it can store a few experiences and allow them to be retrieved at a later time. It can also help with integrating this knowledge without catastrophically interfering \citep{McCloskey1989} with knowledge gleaned from prior experiences, by allowing interleaving of these prior experiences in learning \citep{McClelland1995}. This can potentially occur in a usefully biased way \citep{Kumaran2016}. There may even be interesting computations performed within the hippocampus to support certain types of rapid generalization \citep{Kumaran2012}. \par 
\textbf{Interactive learning \& hypothesis testing:} Humans are able to use our stored experiences to rapidly learn. One example of this is that we often behave as though we are formulating and testing hypotheses, even from a very young age \citep{Sobel2004, Gopnik2014}. We can even take advantage of these hypotheses in order to actively acquire information from the world that is most useful for us \citep[e.g.][]{Markant2014a}. By using our prior knowledge of the world to help interpret new experiences, we are able to make extremely fast inferences about how to understand a new situation. \par
\textbf{Education \& learned flexibility:} However, our ability to reason rapidly is not solely learned on our own. Indeed, a focus of education is preparing us for future learning \citep{Bransford1999}, and flexibility \citep[e.g.][]{Richland2012}. That is, we are explicitly taught to learn increasingly rapidly as education goes on. Elementary school children require months or years of rote practice to learn arithmetic, but college mathematics students are expected to hear a theorem once and then immediately be able to apply it. As noted above, we may not be perfect at these faster learning tasks \citep[e.g.][]{Hazzan1999}. However, adults are much better at them than children, and mathematics graduate students are much better than undergraduates \citep{Weber2001}. The ability to learn and apply new knowledge rapidly develops as we do.Furthermore, as we grow up we also grow better at explaining our actions, and adapting to instructions \citep[e.g.][]{Doebel2015}. Over the course of development, we practice many types of flexibility. \par 
\textbf{Explanations and demonstrations:} Both in education and outside of it, explanations are a key way we learn about the world, because they can succinctly convey rich structure \citep[e.g.][]{Keil2006, Lombrozo2006}. Importantly, explanations can be succinct because they exploit our prior knowledge in order to convey only the information that needs to be clarified (i.e. they follow the pragmatic principle of not being overinformative, expressed by \citet{Grice1975} for communication more generally). We not only learn from hearing explanations, but also from producing them \citep{Chi1989, Chi1994}, and so it is a common pedagogical principle to ask students to generate explanations. Explanations form a key tool for learning. \par
Similarly, we can also learn quite rapidly from demonstrations, which provide another succinct means for conveying important structure in the world. This learning requires applying our prior knowledge to infer what should and should not be generalized, but fortunately we can do this even from a young age, see \citet{VanDamme2002} for example. Both explanations and demonstrations provide powerful tools for learning rapidly. We develop the ability to exploit these tools early in life \citep{Carpenter2005}. \par 
\textbf{Analogical and relational reasoning, and abstraction:} Some researchers have argued that analogical transfer and abstraction form crucial components of our learning \citep[e.g.][]{Gentner2003, Lakoff2008, Gentner2017}. These accounts often focus on fast, explicit transfer of the form explored by \citet{Gick1980}, for example. The structure-mapping algorithm \citep{Falkenhainer1989} proposed for this is based on explicitly searching over possible isomorphisms, which tends to be infeasible in practice. However, there may be ways to implement it efficiently enough that it could be considered for complex cognitive models \citep{Forbus2017}, and in past work I suggested that implicit learning could provide heuristics to dramatically speed up this search \citep{Lampinen2017a}. It's also reasonable to expect this ability to be related to education and other individual factors, since its been observed that features such as fluid intelligence may interact with the type of scaffolding provided to affect explicit analogical transfer \citep{Kubricht2017}. Indeed, older students are often better at transferring knowledge than younger ones \citep[e.g.][]{Chen1999}. This is suggestive of this type of transfer being a learned skill, rather than a cognitive primitive. \par
Much of the work on analogical and relational reasoning also focuses on the benefits of comparing multiple examples, which can lead to more reliable induction of abstractions or schemas and better transfer \citep{Gick1980, Gentner2017}. It has even been suggested that this is a key way to understand the benefits of grounding \citep{Jamrozik2016}. However, in some past work, I found that seeing two different presentations of a mathematical concept lead to better learning overall than seeing either individually, but did not lead to significantly better abstraction of formal principles \citep{Lampinen2017b}. Thus it remains important to ask when reasoning about multiple examples leads to abstraction, and when it does not. One feature that is often important is explicitly considering the relationship between examples \citep{Gentner2017}, but it's likely that the quality of understanding of the examples matters as well. \par 
\textbf{Consciousness and explicit reasoning:} Consciousness is a slippery topic, but unfortunately must be discussed, as it underlies many of the fast-learning systems above. Most of these rely on our ability to explicitly reason about concepts once we have sufficiently high-quality representations of them. The global workspace theory of consciousness \citep{Baars2005, Dehaene2017} is closely aligned  to this perspective. It states that conscious knowledge is precisely that which is globally accessible, and therefore with which we are most flexible. This concords to some degree with the perspectives of \citet{Karmiloff-Smith1986}, who argued that once we re-represent knowledge to be explicit, we can use it more flexibly. \par
However, \citet{Karmiloff-Smith1986} also argued that there were different levels of explicit representation of knowledge, and indeed some consciousness researchers have proposed more graded transitions from implicit to explicit \citep[e.g.][]{Cleeremans2002}. Computational models of graded transistions have been proposed, where explicit knowledge is essentially learned by a separate system which reasons over implicitly learned representations \citep{Cleeremans2014}. This fits more with the work reviewed above showing a graded transition to explicit knowledge built upon implicit understanding grounded in percetual-motor features \citep[e.g.][]{Goldin-Meadow1993}, procedures \citep[e.g.][]{Hazzan1999}, or more basic concepts \citep{Wilensky1991, Patel2018}. Thus, when thinking about the relationship between implicit and explicit knowledge is unavoidable, we will take the perspective that explicit reasoning is built upon implicitly learned representations. \par 
Another place where explicit reasoning plays a role is in helping us to understand and learn from our own mistakes. For example, \emph{deliberate practice} (targeting specific aspects of performance for improvement) has been claimed to be key to developing expertise \citep{Ericsson1993, Ericsson2017}. Yet to engage in deliberate practice requires meta-knowledge about what needs to be improved, and indeed this abstract understanding is an important component of expert knowledge \citep{Feltovich2012}. \par
\textbf{Summary:} We possess fast learning systems that are engineered by evolution, such as the hippocampus, and ones that are culturally transmitted, such as our ability to follow instructions in our native language(s). Together, they allow us to infer a great deal from little information, by leveraging our slowly-accumulated prior knowledge. They also allow us to flexibly adapt our behavior through practiced algorithms like following instructions. \par 

\subsubsection{Interactions between fast and slow learning systems} \label{fast_slow_interactions}
I claim that most transfer arises as a synergy between different kinds of learning across different timescales. In particular, the knowledge we have accumulated over our lifetimes (part of which has been accumulated by our cultures over millenia) allows us to constrain the hypothesis space for new learning, so that we can make accurate inferences from a few examples in a new situation. \par 
From my perspective, this slowly-learned knowledge of the world can take multiple forms. It can occur in the mapping from inputs to our awareness, for example in visual cortex neurons which adapt to the regularities encountered over development \citep{Barlow1975}. However, it can also occur in the systems that implement higher-level and more rapid computations.\footnote{Clearly certain kinds of knowledge will lend themselves more easily to being learned in development and others will lend themselves more easily to being culturally transmitted or even learned by evolution. For the most part, I will generally assume that this knowledge emerges from experience or is culturally conveyed rather than being built in \citep{Hansen2017}, but my conclusions will mostly be agnostic to the origins of any particular piece of knowledge.} For example, the results on transfer in artificial grammar learning described above \citep{Tunney2001} or the results on transfer of simple harmonic oscillator strategies \citep{Day2011} show that humans are able to transfer knowledge at the level of structures or algorithms. The limits of this transfer are as yet unclear, as are the time-scales over which different kinds of transfer can occur; some of the work in my dissertation will attempt to explore these issues.\par  
\textbf{Limitations \& tradeoffs:} Of course, there are trade-offs to relying on transfer and prior knowledge. When new tasks are not well aligned with our prior knowledge, relying on prior knowledge can actually interfere with learning. For example, this is one piece of the argument that we made \citep{Lampinen2017b} to explain the results of \citet{Kaminski2008}. This is an illustration of the broader phenomenon of negative transfer -- interference effects produced by transferring between non-isomorphic domains. A wide variety of studies have observed this type of phenomenon \citep[e.g.][]{Luchins1942, Landrum2005}. Our prior knowledge can be detrimental in some situations. \par
This brings us back to the broader point raised by \citet{Detterman1993} above, that humans are often unable to efficiently or flexibly transfer knowledge to new situations. Instead, this must be a goal of education \citep{Bransford1999}, and learning what is transferable may require developmental time \citep{Lampinen2017a} if the representations of the tasks are not sufficiently good to support faster transfer. We can be efficient and flexible when our prior learning has set us up to be. We are not always. We can be mislead by mismatches between the past and the present, or we can simply fail to find the correct analogy.\par

\subsection{Steps towards flexibility in deep learning}

A great deal of recent work in machine learning can be seen as attempts to build machine-learning systems with greater flexibility. In particular, much of this work has tried to allow them to learn from fewer examples, or generalize better to data that weren't seen during training. This work typically follows one of two approaches. The first, multi-task learning, focuses on learning multiple tasks with a single model, in the hope that the additional constraints on the model's representations will cause it to learn more rapidly or generalize better. The second approach, meta-learning, focuses on learning how to learn tasks, in the hopes of learning much faster and generalizing better from extremely small samples. I will give a brief overview of both these literatures in this section. \par

\subsubsection{Multi-task learning}

Multi-task learning is generally related to the ``slow'' learning systems I described in humans. Typically, parameters are partially shared between the two tasks, and these shared parameters are learned over long time-scales. This can be done either in a sequential fashion (where you use one task to pre-train the network for another), or simultaneously (where you learn multiple tasks at the same time or on alternating gradient steps). Auxiliary tasks need not be of the same type as the main task, for example reinforcement learning tasks can be supplemented with auxiliary supervised tasks like temporal autoencoding \citep[e.g.][]{Hermann2017}, or unsupervised tasks can be used to pre-train for supervised ones \citep[e.g.][]{Wu2018}. \par
\textbf{Pre-training:} One example of sequential multi-task learning is the extremely common practice of pre-training a network on some canonical task in order to use one of its hidden layers as a feature for some other related task. For example, pre-training on ImageNet \citep{Deng2009} is often seen as a useful general feature extractor for vision tasks \citep{Huh2016}, even for quite different transfer domains \citep[e.g.][]{Marmanis2016}. There is still active research on how to optimally pre-train features for various goals \citep[e.g.][]{Wu2018}. \par    
However, pre-training is used on more than just vision tasks. In natural language processing (NLP) applications, the representations of words is often pre-trained on co-occurrence prediction tasks \citep[e.g.][]{Pennington2014}. The more general language modeling task (predicting words conditioned on past input) can serve as unsupervised pretraining for many tasks \citep[e.g.][]{Radford2019}. In AlphaGo \citep{Silver2016}, the networks were pre-trained to predict expert go-players' moves, and then were tuned from that starting point using reinforcement learning. The principle that pre-training a network can allow it to generalize better from smaller training sets appears to be quite general, although there is still some debate and ongoing research \citep[e.g]{He2018, Silver2017}. \par
There are also many remaining questions about how other features of training interact with transfer. Some researchers have argued that \emphe{disentangled representations} will be helpful for future tasks \citep{Higgins2018}, while others have argued that disentangled representations are hard to define, and that the evidence that they are useful is weak \citep{Locatello2019}. Other some recent work suggests that some forms of regularization may actually harm transfer \citep{Kornblith2019}. One possible explanation for this is that regularization is too compressive in the transfer setting -- it may compress away some real features that are useful for the transfer task, but not for the source task. However, this might be different if the tasks were trained simultaneously (see below) rather than in a pre-training setting. Understanding when this occurs, and how to balance the generalization benefits of regularization with transfer benefits will be an important area for future work. \par

\textbf{Curriculum learning:} A more general kind of pre-training is curriculum learning \citep{Bengio2009} -- the idea that training models on a structured progression of tasks can improve generalization. Pre-training on a single task is essentially a very simple curriculum. The idea of curricula began with \citet{Elman1993}, but was debated \citep[e.g.][]{Rohde1997}. However, subsequent work has demonstrated the importance of curricula both in toy settings \citep{Gulcehre2013} and in much more complicated models \citep[for example][discussed below]{Graves2016}. \par
Curriculum learning of course raises another issue: what if you want your model to perform well at several tasks? If you switch to training on a new task, it may catastrophically interfere with your ability to perform a previous task \citep{McCloskey1989}. The complementary learning systems perspective \citep{McClelland1995, Kumaran2016} was intended in part to address this issue. A number of other approaches have also been proposed recently, based on ideas like preserving parameters from updates proportionally to how important they are for old tasks \citep{Kirkpatrick2016}, or learning tasks separately but distilling the knowledge into a single network later \citep{Rusu2015}, or by trying to use unsupervised learning to find compact representations and allocate new tasks so that they don't interfere \citep{Achille2018a}. There are also some memory-based approaches discussed in section \ref{meta_learning_sec} that can ameliorate this problem. Thus there are a variety of approaches that can address catastrophic interference, while still maintaining the benefits of curriculum learning. \par

\textbf{Simultaneous multi-task learning:} However, many multi-task learning approaches train on the tasks simultaneously rather than sequentially. For example, simultaneously training a natural language translation system to do image captioning in the target language improves its translation performance \citep{Luong2016}. Even training it to translate between multiple language pairs is beneficial \citep{Dong2015}. This can even lead to zero-shot generalization to translation between language pairs never seen together in training \citep{Johnson2016a}. \par 
The idea of multi-task learning has proven even more critical in Reinforcement Learning (RL), where auxiliary tasks have been suggested as a key approach to overcoming the problem of reward sparsity \citep[e.g.][]{LeCun2016}. They have been used this way on a variety of RL tasks, for example in grounded language learning \citep{Hermann2017}. \par
The broad observation that deep networks will learn representations that represent shared structure in the tasks they perform, and can exploit this shared structure to generalize better, is not new. It was observed at least as long ago as \citet{Hinton1986}, and has continued to intrigue researchers since \citep[e.g.][]{Lampinen2017a}. In particular, it is a key feature that separates deep networks from simpler statistical learning architectures, and allows them to uncover and exploit deep structure in the world \citep{Rogers2008}. This is key to some of the kinds of transfer that deep networks demonstrate, and has been substantially helpful in the machine learning work above. Thus the benefits of multi-task transfer should not be neglected when considering deep learning models of cognition. \par 

\textbf{Learning which parameters to share:} Most the work above simply fixes architectures with pre-specified shared and unshared weights. However, there are other approaches that attempt to learn which weights to share. The work of \citet{Achille2018a}, referenced above, is one example of this.  Other authors have considered using evolutionary algorithms to decide which subsets of modules should be shared \citep{Fernando2017}. Some other approaches can also be seen from this perspective, for example choosing a sparse subset of modules for each forward pass \citep{Shazeer2017} or using a HyperNetwork to generate the weights for other networks \citep{Ha2016}. Both these can be seen as a way of learning which weights should be shared or separate between different ``sub-tasks'' of a task. Some of the work discussed in section \ref{meta_learning_sec} can also be viewed as learning what parameters should be shared and which should be separate. While in principle a fully-shared network could learn which parameters to share just by gradient descent, in practice a more structured approach to this problem can be useful. \par 

\textbf{Summary:} To summarize, curriculum and multi-task learning can help set up representations that allow deep learning models to generalize better from less data, or to learn tasks that would not otherwise be learnable. This is because the additional constraints imposed by auxiliary or pre-training tasks on the networks representations help it to uncover the true underlying structure in the world. While multi-task learning does not support all the kinds of flexibility that humans demonstrate, it is a key piece of the puzzle of how deep networks can learn faster and generalize better. \par

\subsubsection{Meta-learning \& related approaches} \label{meta_learning_sec}

The fundamental insight of meta-learning is that there is a continuum between data and tasks. We can interpret each (input, target) tuple as a simple task, and we can interpret subsets of a dataset as sub-tasks, for example all the dog images contained within ImageNet form a semantically distinguishable sub-task of the overall task. Analogously, we can often interpret a single task as being just a point in a larger space of tasks. Most meta-learning models exploit these insights by having the architecture adapt to a given task within its activations instead of its weights, just as a CNN would adapt to the fact that its current input was a dog image rather than a tree image within its activations. Learning to adapt to new tasks in this way has been shown to allow for much more efficient learning on new tasks, and may be key to modeling human intelligence \citep{Hansen2017}. \par 
\textbf{Basic meta-learning:}
The basic meta-learning approach (representing a task within activations) has been applied to many settings. For example, it has been used to learn to classify new images based on single positive exemplars of each class \citep{Vinyals2016}. It has also been used to teach recurrent networks to solve simple reinforcement learning problems \citep{Duan2016, Wang2016a, Stadie2018}. \par
There have been many variations on this approach. Some meta-learning work has exploited both slow and fast weights with some success \citep[e.g.][]{Munkhdalai2017}, taking one perspective on the dichotomy I proposed above. Many approaches have exploited other tricks that are broadly useful in machine learning. For example, some work has leveraged unlabelled examples along with a few labelled ones to yield better meta-learning results \citep[e.g.][]{Ren2018}. Other work has shown that attention-based models are useful \citep{Reed2017}, as in many other machine-learning applications \citep[e.g.][]{Vaswani, Gregor2015}. \par
\textbf{Memory-based:} There are a variety of meta-learning approaches that are based on a non-parametric memory, and generally some form of key-value attentional lookup over it. A general extension of the basic meta-learning approach to the case with memory is given in \citet{Santoro2016}. Other approaches are based on using memory only at testing, e.g. by tuning the network rapidly to perform well on similar examples, as proposed by \citet{Sprechmann2018}. \par 
More flexible variants have also been proposed. For example, the differentiable neural computer (DNC), proposed by \citet{Graves2016} is able to receive a graph structure as inputs, learns to store it in memory, and then learns to use that stored information to solve problems like computing shortest paths. This can effecetively be seen as meta-learning -- the architecture has the flexibility to learn and reason from new knowledge rapidly. However, this flexibility remains fundamentally within the computations done for a task which is slowly learned, and does not by itself allow the more general flexibility that humans exhibit. \par
\textbf{Language:} There is some work that has explored related problems from a language-based perspective. For example, \citet{Larochelle2008} considered the general problem of behaving in accordance with language instructions as simply asking a model to adapt its response when conditioned on different ``instruction'' inputs. More recently, there has been a productive line of research in using language to compose network modules for question answering \citep{Andreas, Andreasa}. There has also been some work on reinforcement learning systems that learn to follow natural language instructions in a simple enviroment \citep{Hermann2017}. \par
More recently, \citet{Radford2019} showed that a language model trained on an extremely large corpus of curated websites actually acquires some meta-like abilities, for example the ability to translate languages ``zero-shot'' (i.e. when conditioned on examples of translation pairs and then given a new sentence, it produces a translation). It is also able to summarize, answer questions, etc. It does this presumably because the corpus contains some translation pairs in context or summaries on a page, and so those tasks essentially compose a small part of the language modeling problem. It's worth noting that the performance on these tasks is rudimentary, and far from models that are trained for these tasks in a supervised way, but it is still an impressive demonstration of the power of prediction to extract deep latent structure in the world, and the power of broad enough training data distributions to teach flexibility. \par  
\textbf{Demonstrations:} The issue of learning from demonstrations has also been considered in the machine learning literature for some time, because of its potential applications in problems where we know what behavior we want, but not how to encode it. There the problem has generally been referred to as ``inverse reinforcement learning'' \citep{Ng2000}, i.e. the problem of inferring a value function from observed behavior. A large number of approaches to this problem have been proposed \citep[e.g.][]{Ng2000, Abbeel2004}. Recently, approaches combining meta-learning and deep learning have achieved some success on this. For example, \citet{Finn2016} present an algorithm which can learn to infer a reasonable approximation of the objective function from a single demonstration. This work shows that neural networks can learn to learn from demonstrations. \par
\textbf{Relational and analogical reasoning:} There are a number of other approaches that attempt to explicitly build relational priors or abstraction into deep-learning architectures. Relation networks \citep{Santoro2017} build in this prior by having the architecture explicitly relate different parts of the input, and achieve better performance on answering relational questions about visual scenes. Architectures that directly allow for true relational binding can be beneficial for a variety of applications, especially natural language processing or symbolic reasoning \citep[e.g.][]{Smolensky1990, Smolensky2014, Huang2017}. More generally, graph-structured networks or other relational inductive biases have been suggested as a promising direction in deep learning \citep{Battaglia2018}. How relational inductive biases can benefit learning is an important direction for future research. \par 
However, relational reasoning is constrained by training as well as the architecture. For example, choosing the negative examples that a network learns from to explicitly contrast relational hypotheses can help to yield more relational reasoning \citep{Hill2019}. Exploring how architecture and training interact to produce relational reasoning will be an important future direction. \par
\textbf{Abstraction:} There has also been some work on explicitly building in abstraction capabilities to machine learning systems. For example, in reinforcement learning the idea of options \citep{Sutton1999} and hierarchical reinforcement learning more broadly \citep[e.g.][]{Botvinick2009} are essentially encapsulations of temporal abstraction, where a sequence of actions can be represented as a single higher-level action. For example, we can think of going to the office as a single action, rather than a sequence of many steps. Similar attempts have been made to allow deep learning models to share knowledge across tasks, with some success \citep[e.g.][]{Tessler2016}. \par 
There have also been a variety of attempts to combine deep learning methods with more programming-like approaches. For example, Neural Programmer-Interpreters \citep{Reed2015} essentially endow a recurrent network with the ability to call sub-routines, and a stack of memory for these sub-routines to use. Applying these ideas to meta-learning problems has been reasonably successful, especially with carefully chosen algorithms for integrating knowledge across tasks \citep[e.g.]{Devlin2017}. Similar techniques have been applied to many domains, such as learning from demonstrations \citep[e.g.][]{Xu2017a}. Combining the old ideas of cognition as executing symbolic programs \citep{Newell1961} with the techniques of deep learning can yield improvements in flexibility. \par  
However, most of these methods are still not as universally flexible as humans. The number of abstractions is usually fixed, often abstractions cannot be composed from other abstractions, and abstractions are inflexible to other demands. For example, a system that has learned an option for walking to a goal will not necessarily be able to change to running to the goal without learning this option from scratch. Thus there are still limitations to these approaches at present. \par 
\textbf{Other work:} There is a variety of other work that has exploited different perspectives on meta-learning. Some of this work could be useful for thinking about flexibility. For example, \citet{Finn2017a} proposed Model-Agnostic Meta Learning (MAML), an approach based on optimizing the model so that it could adapt well to a new task in a few gradient steps, and this work has led to many follow-ups \citep[e.g.][]{Finn2017, Finn2018}. \citet{Xu2018} proposed using meta-learning to adapt hyperparameters of reinforcement learning algorithms across tasks. Both of these approaches allow for better adaptation to new tasks or environments. \par
In addition, there has been some work showing that basic neural network models can adapt rapidly to new data that is consistent with prior knowledge, simply by optimizing weights specific to that data while freezing the remaining weights of the network \citep{Rumelhart1993}. This approach only works if there are weights that are specific to the new item(s), so it is not a general kind of flexibility. Nevertheless, this approach has been applied to understand human semantic cognition \citep{Rogers2004}. More recently, I applied it to one-shot and few-shot learning of words in a language-modeling task \citep{Lampinen2018a}. Thus under some circumstances this approach can yield a certain kind of flexibility, even at the scale of large machine learning tasks. This is more evidence of the general point that information which is consistent with prior knowledge can be rapidly integrated \citep{McClelland2013}. \par 
\textbf{Unintentional ``flexibility'':} There has also been some interesting work on flexibility that emerges accidentally under standard training of deep learning systems. In particular, adversarial examples \citep{SzegedyAdv} are cases when adding a very small perturbation to an input can radically alter the network's output. This is a kind of flexibility, but it is not the desired kind. Instead, these appear to be evidence for the fact that deep networks are inherently chaotic systems, which can respond in surprisingly sensitive ways to their inputs. However, it's worth noting that humans can be susceptible to more extreme adversarial perturbations derived on deep networks \citep{Elsayed2018}. Furthermore, adversarial examples can be exploited, e.g. for better training \citep{Goodfellow2015}. \par 
\citet{Elsayed} demonstrated an even more interesting type of unintentional flexibility: deep networks can be ``reprogrammed'' by an input to solve a different task.\footnote{Although not one completely unrelated to the main task the network was trained on -- the network was trained on a vision task, and their reprogrammed tasks were just other vision tasks. It would be interesting to explore the limits of this ``reprogrammability.''} This is a step closer to the flexibility that humans have, but the ``reprogramming'' inputs have to be derived via an optimization process, and tend to be uninterpretable. Thus there is no systematicity in this flexibility. However, my interpretation of these results is that they are encouraging evidence that these models have the capacity to be extremely flexible under appropriate conditions. All that is needed is to train this flexibility to be more systematic. \par  
\textbf{Summary:} To summarize, meta-learning has made progress on several fronts. It is starting to solve the small data problem, by allowing networks to learn efficiently from a small number of examples \citep[e.g.][]{Wang2016a}. At the other extreme of very large data, deep networks can generalize to some extent to tasks which are only hinted at by the trained task distribution \citep[e.g.][]{Radford2019}. However, there are a number of key features of human flexibility that remain to be explained. In the next section, I will relate transfer and flexibility in humans and deep networks, and discuss what features are still missing. \par 

\subsection{Relating flexibility in humans and neural networks}

The encouraging progress on multi-task and meta-learning in recent years suggests that cognitive models exploiting these techniques may help explain human flexibility and transfer \citep{Hansen2017}. In this section, I will attempt to relate the aspects of human and network flexibility that I outlined in the previous sections. \par 
First, it generally seems that the division between fast and slow transfer is applicable both to the machine learning literature (meta-learning vs. multi-task) and to human transfer, as we highlighted above \citep[and in prior work, namely][]{Lampinen2017a}. Following complementary learning systems, I suggest that broadly our slow learning of structure in the world happens over the course of developmental time in a multi-task fashion. Algorithmically, this occurs because parameters in our brain come to represent and exploit structural similarities across the many tasks we experience. We also practice doing fast learning over these slowly-learned representations, in educational settings as well as in everyday experience more broadly. Thus I think that cognitive models should employ both slowly-learned shared representations, and a system that allows for rapid and flexible reasoning over them. I argue that incorporating both aspects will be key to modeling the full range of human flexibility. \par 
It is also important to note the differences between the systematic, structured training that humans encounter in culturally-constructed educational systems, and the unstructured, IID training that deep learning models canonically receive. While curriculum learning addresses some of the sequential learning in education, and meta-learning addresses part of the learning-to-learn aspect, the full training on flexibility is generally missing. For example, humans learn a great deal from explaining as well as simply doing, yet we rarely train our machine learning models to explain their actions. Given the sensitity to training data that both humans and neural networks display, we cannot expect deep learning models to capture human behavior completely under drastically different learning regimes. How to train deep models in more human-like ways is an important direction for future work.  \par
In summary, I think deep learning models remaining promising cognitive models. They have successfully modeled a wide range of phenomena ranging from low-level neural activity to cognition. Furthermore, they are compelling models in particular of high-level cognitive phenomena, because they are some of the only systems to successfully achieve human performance at difficult tasks like visual recognition or playing go. They even have some inherent (if often unstructured and unintentional) flexibility, as indicated by adversarial examples and reprogramming. \par
I suggest that humans are similarly flexible. I suggest that the reason our flexibility is less chaotic is that we learn over the course of development and education to exploit our flexibility in systematic ways, in order to be adaptable to new tasks and situations. A very weak example of this in machine learning is given by \citet{Radford2019}, discussed above, where training a language model on a large enough text distribution gives some generalization to related tasks. However, this network required far more training than could be assumed for humans, and still lacked some of the flexibility that humans have. I suggest that this is because of the lack of multiple tasks to constrain the representations, the lack of an architecture explicitly designed to allow synergies between fast and slow learning, and the lack of the systematic, structured training that humans experience. \par 

\subsubsection{What's still missing?}

For the reasons highlighted above, some flexibility is still missing from deep-learning systems. Although they can often learn a new task from few examples, most demonstrations of this have involved sampling tasks that are within a dense region of the training task distribution. Furthermore, humans have a great deal more flexibility than simply learning rapidly. We can decide how to behave on a new task based on natural language instructions we are given. We can also adapt our behavior on a task based on feedback about our actions, and can jointly learn from language and examples better than we can learn from either alone. \par
We can also remap our behavior on tasks based on instructions or examples of tasks. For example, if we are told to try to lose a game we have previously been trying to win, this is an easy task for us. It would be quite difficult for any contemporary reinforcement learning model to invert its value function. If we are given examples of task mappings, e.g. we've played chess on a smaller board and checkers on a smaller board, we are able to remap our strategies for go to play on a smaller board. That is, we can flexibly map between behavioral strategies on different tasks based on either linguistic or (task) exemplar input. The meta-learning systems I have reviewed do not yet have this flexibility. \par
This is related to the more general point that humans have the ability to flexibly reason across levels of abstraction. For example, humans can relate between examples of a concept and what they imply about the overall concept, e.g. as counter-examples to universal properties. With training, we can even reason flexibly across complex hierarchies of abstraction, as when thinking about the mathematical concepts of numbers, sets, functions, and categories. We are able to recursively build abstractions on top of abstractions (though this is often a slow process). By contrast, deep learning models typically represent different levels of abstraction separately, e.g. at separate layers of a feed-forward architecture. This limits the flexibility of reasoning between them (the only available mapping is the canonical transformation given by the weights), and because the abstraction is built in to the architecture, it can not be applied recursively. Similarly, we can reason both about data and the computations we perform over data, whereas most deep learning architectures restrict their knowledge of computations to weights which they have no explicit access to. This limits the flexibility and representational capacity of these networks. \par 
To summarize, we can flexibly map between data, language, and tasks, across different levels of abstraction. Contemporary deep learning architectures lack this full range of flexbility, although certain models have achieved some promising steps toward certain aspects of it. In section \ref{eml_sec}, I will propose a new architecture that I think comes closer to achieving human-like flexibility. In the remainder of section \ref{RR_sec}, I will describe some past work and future directions that explore the extent of this human flexibility, and work investigating the benefits of multi-task learning in neural networks. \par 
